Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-01-17 paper.tex
More minor changes to reduce plagiarism

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{natbib}

@@

This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load tot he user, given humans' natural ability to determine a sound source 3D positions.
By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
In this case, only the pan and elevation positions are given to the user to instruct them to point the camera towards a target object or visual feature.
However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted, since they are placed on the user's cheekbones and bypass the ears outer structure.
We bypass this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in that dimension.
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
The majority of these systems rely on one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\citep{arditi2013user}.
However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.

@@

The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \Cref{fig:cam-coords}.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.

@@

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{natbib}
\usepackage{todonotes}

@@

\todo{edit start}
This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load tot he user, given humans' natural ability to determine a sound source 3D positions.
By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
In this case, only the pan and elevation positions are given to the user to instruct them to point the camera towards a target object or visual feature.
However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted by a human, since they are placed on the user's cheekbones and bypass the ear's outer structure.
We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in that dimension.
\todo{edit stop}
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

\todo{edit start}
Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
The majority of these systems rely on one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\citep{arditi2013user}.
However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.
\todo{edit stop}

@@

The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \Cref{fig:cam-coords}.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}. 
This interface was implemented and evaluated in previous work~\citep{lock2019bone}.

@@

\subsection{Participant Feedback}

\todo{include subjective feedback?}
